On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-30 paper/paper.tex
Clean up some less relevant TODOs and minor formatting

\subsection{Translation Example}
\begin{todo}
  Does it make sense for this to be a subsection of the intro?
\end{todo}

@@

\begin{todo}
  Look into \ttt{generic-sop} and compare then cite corresponding paper.
\end{todo}

@@

\begin{todo}
  Should we make a synonym for this constraint since it is used in
multiple places? Like this:
\begin{lstlisting}
type CanonicalIsIdem t =
  ERepTy (ERepTy t) ~ ERepTy t
\end{lstlisting}
\end{todo}

@@

The \verb|Church'| type forms a large part of the foundation of the pattern
matching aspect of the \verb|E| type. A correspondence between the two
is given in the table below.\\

@@

\clearpage
\section{Related Work}
\begin{todo}
  Does this need more fleshing out?
\end{todo}

>>>>

\subsection{Translation Example}

% \begin{todo}
%   Does it make sense for this to be a subsection of the intro?
% \end{todo}

@@

% \begin{todo}
%   Look into \ttt{generic-sop} and compare then cite corresponding paper.
% \end{todo}

@@

% \begin{todo}
%   Should we make a synonym for this constraint since it is used in
% multiple places? Like this:
% \begin{lstlisting}
% type CanonicalIsIdem t =
%   ERepTy (ERepTy t) ~ ERepTy t
% \end{lstlisting}
% \end{todo}

@@

The \verb|Church'| type forms a large part of the foundation of the pattern
matching aspect of the \verb|E| type. A rough correspondence between the two
is given in the table below.\\

@@

\clearpage
\section{Related Work}

% \begin{todo}
%   Does this need more fleshing out?
% \end{todo}
